Probabilistic Catalogs for Crowded Stellar Fields

### 2012-11-20 paper/ms.tex
It's not "fully Bayesian" if you use MCMC

In this paper we have developed and demonstrated a fully Bayesian approach to
making catalogs from astronomical images in the case where the image contains
only stars (or other point sources). The key idea is that instead of computing
a single catalog, the method creates a posterior probability distribution on
the space of possible catalogs that represents our state of knowledge about
the presence and properties of objects in the image. When this is done, the
uncertainties in the imaging are accurately propagated through to scientific
conclusions, for example about the luminosity function of the stars.
This approach was contrasted with a standard method of running \sex~and then
fitting a luminosity function to the fluxes in the catalog. This latter approach
was shown to produce incorrect inferences about the luminosity function.

>>>>

In this paper we have developed and demonstrated a Bayesian approach to
making catalogs from astronomical images in the case where the image contains
only stars (or other point sources). The key idea is that instead of computing
a single catalog, the method creates a posterior probability distribution on
the space of possible catalogs that represents our state of knowledge about
the presence and properties of objects in the image. When this is done, the
uncertainties in the imaging are accurately propagated through to scientific
conclusions, for example about the luminosity function of the stars.
This approach was contrasted with a standard method of running \sex~and then
fitting a luminosity function to the fluxes in the catalog. This latter approach
was shown to produce incorrect inferences about the luminosity function.
